Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-06 Paper.tex
Biblio: moved dates to the note field, fixed author fields, added last  accessed (which also shows in the Wayback link), added filetea links for pages not able to be saved (or at least not properly) by the Wayback Machine. Removed some Wikipedia references, and I will remove more.
Paper.tex: added a note for the difficulty, with citations.

\begin{description}\hypertarget{H p}{
\item[parentHash] The Keccak 256-bit hash of the parent block's header, in its entirety; formally $H_\mathbf{p}$.}
\item[ommersHash] The Keccak 256-bit hash of the ommers list portion of this block; formally $\hyperlink{H o}{H_\mathbf{o}}$.\hypertarget{H c}{
\item[beneficiary] The 160-bit address to which all fees collected from the successful mining of this block shall be transferred; formally $H_\mathbf{c}$.}
\item[stateRoot] The Keccak 256-bit hash of the root node of the state \hyperlink{trie}{trie}, after all transactions are executed and finalisations applied; formally \hyperlink{H r}{$H_\mathbf{r}$}.
\item[transactionsRoot] The Keccak 256-bit hash of the root node of the \hyperlink{trie}{trie} structure populated with each transaction in the transactions list portion of the block; formally \hyperlink{H t}{$H_\mathbf{t}$}.
\item[receiptsRoot] The Keccak 256-bit hash of the root node of the \hyperlink{trie}{trie} structure populated with the receipts of each transaction in the transactions list portion of the block; formally \hyperlink{H e}{$H_\mathbf{e}$}.
\item[logsBloom] The Bloom filter composed from indexable information (logger address and log topics) contained in each log entry from the receipt of each transaction in the transactions list; formally \hyperlink{H b}{$H_\mathbf{b}.$}\hypertarlink{H d}{
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_\mathbf{d}$}.\hypertarget{H i}{
\item[number] A scalar value equal to the number of ancestor blocks. The \hyperlink{GenesisBlock}{genesis block} has a number of zero; formally $H_\mathbf{i}$.}\hypertarget{H l}{
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_\mathbf{l}$.}\hypertarget{H g}{
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_\mathbf{g}$.}\hypertarget{H s}{
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally {$H_\mathbf{s}$}.}\hypertarget{H x}{
\item[extraData] An arbitrary byte array containing data relevant to this block. This must be 32 bytes or fewer; formally $H_\mathbf{x}$.}\hypertarget{H m}{
\item[mixHash] A 256-bit hash which proves combined with the nonce that a sufficient amount of computation has been carried out on this block; formally $H_\mathbf{m}$.}
\hypertarget{block nonce}{\hypertarget{H n}{
\item[nonce] A 64-bit hash which proves combined with the mix-hash that a sufficient amount of computation has been carried out on this block; formally $H_\mathbf{n}$.}}
\end{description}
\hypertarget{B U}{
The other two components in the block are simply a list of ommer block headers (of the same format as above), $B_\mathbf{U}$, and a series of the transactions, $B_\mathbf{T}$. Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (B_H, B_\mathbf{T}, B_\mathbf{U})
\end{equation}}

@@

The values stemming from the computation of transactions, specifically the \hyperlink{Transaction Receipt}{transaction receipts, $B_\mathbf{R}$}, and that defined through the transaction's \hyperlink{Pi}{stateR-accumulation function, $\Pi$}, are formalised later in section \ref{sec:statenoncevalidation}.

@@

The canonical gas limit $\hyperlink{H l}{H_\mathbf{l}}$ of a block of header $H$ must fulfil the relation:
\begin{eqnarray}
& & \hyperlink{H l}{H_\mathbf{l}} < {P(H)_H}_\mathbf{l} + \left\lfloor\frac{{P(H)_H}_\mathbf{l}}{1024}\right\rfloor \quad \wedge \\
& & \hyperlink{H l}{H_\mathbf{l}} > {P(H)_H}_\mathbf{l} - \left\lfloor\frac{{P(H)_H}_\mathbf{l}}{1024}\right\rfloor \quad \wedge \\
& & \hyperlink{H l}{H_\mathbf{l}} \geqslant 125000
\end{eqnarray}

@@

One plague of the Bitcoin world is ASICs. These are specialised pieces of compute hardware that exist only to do a single task (\cite{ASICSmithMJS}, \cite{ASICWiki}). In Bitcoin's case the task is the SHA256 hash function (\cite{ASICbitcoinwiki}). While ASICs exist for a proof-of-work function, both goals are placed in jeopardy. Because of this, a proof-of-work function that is ASIC-resistant (i.e. difficult or economically inefficient to implement in specialised compute hardware) has been identified as the proverbial silver bullet.

@@

\item[Ethereum Browser] (aka Ethereum Reference Client) A cross-platform GUI of an interface similar to a simplified browser (a la Chrome) that is able to host sandboxed applications whose backend is purely on the Ethereum protocol, which is known as Mist since 8 July 2016 (\cite{Mist}).

@@

$G_{\mathrm{txcreate}}$ & 32000 & This is paid by all contract-creating transactions after the {\it Homestead transition}.}\hypertarget{Gtxdatazero}{\\

>>>>

\begin{description}\hypertarget{H p}{
\item[parentHash] The Keccak 256-bit hash of the parent block's header, in its entirety; formally $H_\mathbf{p}$.}
\item[ommersHash] The Keccak 256-bit hash of the ommers list portion of this block; formally $\hyperlink{H o}{H_\mathbf{o}}$.\hypertarget{H c}{
\item[beneficiary] The 160-bit address to which all fees collected from the successful mining of this block shall be transferred; formally $H_\mathbf{c}$.}
\item[stateRoot] The Keccak 256-bit hash of the root node of the state \hyperlink{trie}{trie}, after all transactions are executed and finalisations applied; formally \hyperlink{H r}{$H_\mathbf{r}$}.
\item[transactionsRoot] The Keccak 256-bit hash of the root node of the \hyperlink{trie}{trie} structure populated with each transaction in the transactions list portion of the block; formally \hyperlink{H t}{$H_\mathbf{t}$}.
\item[receiptsRoot] The Keccak 256-bit hash of the root node of the \hyperlink{trie}{trie} structure populated with the receipts of each transaction in the transactions list portion of the block; formally \hyperlink{H e}{$H_\mathbf{e}$}.
\item[logsBloom] The Bloom filter composed from indexable information (logger address and log topics) contained in each log entry from the receipt of each transaction in the transactions list; formally \hyperlink{H b}{$H_\mathbf{b}.$}\hyperlink{H d}{
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_\mathbf{d}$}.\hypertarget{H i}{
\item[number] A scalar value equal to the number of ancestor blocks. The \hyperlink{GenesisBlock}{genesis block} has a number of zero; formally $H_\mathbf{i}$.}\hyperlink{H l}{
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_\mathbf{l}$.}\hypertarget{H g}{
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_\mathbf{g}$.}\hypertarget{H s}{
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally {$H_\mathbf{s}$}.}\hypertarget{H x}{
\item[extraData] An arbitrary byte array containing data relevant to this block. This must be 32 bytes or fewer; formally $H_\mathbf{x}$.}\hypertarget{H m}{
\item[mixHash] A 256-bit hash which proves combined with the nonce that a sufficient amount of computation has been carried out on this block; formally $H_\mathbf{m}$.}
\hypertarget{block nonce}{\hypertarget{H n}{
\item[nonce] A 64-bit hash which proves combined with the mix-hash that a sufficient amount of computation has been carried out on this block; formally $H_\mathbf{n}$.}}
\end{description}
\hypertarget{B U}{
The other two components in the block are simply a list of ommer block headers (of the same format as above), $B_\mathbf{U}$, and a series of the transactions, $B_\mathbf{T}$. Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (B_H, B_\mathbf{T}, B_\mathbf{U})
\end{equation}}

@@

The values stemming from the computation of transactions, specifically the \hyperlink{Transaction Receipt}{transaction receipts, $B_\mathbf{R}$}, and that defined through the transaction's \hyperlink{Pi}{state-accumulation function, $\Pi$}, are formalised later in section \ref{sec:statenoncevalidation}.

@@

Note that \mindifficulty is the difficulty of the genesis block. The effect of the difficulty parameter \homesteadmod on a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. \expdiffsymb results in the difficulty increasing every 10000 blocks, which also stabilises the time difference between blocks, as computation power becomes more efficient, \eg with Moore's Law (\cite{Multichain}, \cite{Moore}).

\hypertarget{H l}{
The canonical gas limit $\hyperlink{H l}{H_\mathbf{l}}$ of a block of header $H$ must fulfil the relation:
\begin{eqnarray}
& & \hyperlink{H l}{H_\mathbf{l}} < {P(H)_H}_\mathbf{l} + \left\lfloor\frac{{P(H)_H}_\mathbf{l}}{1024}\right\rfloor \quad \wedge \\
& & \hyperlink{H l}{H_\mathbf{l}} > {P(H)_H}_\mathbf{l} - \left\lfloor\frac{{P(H)_H}_\mathbf{l}}{1024}\right\rfloor \quad \wedge \\
& & \hyperlink{H l}{H_\mathbf{l}} \geqslant 125000
\end{eqnarray}}

@@

One plague of the Bitcoin world is ASICs. These are specialised pieces of compute hardware that exist only to do a single task (\cite{ASICSmithMJS}, \cite{ASICWiki}). In Bitcoin's case the task is the SHA256 hash function (\cite{Courtois2014}). While ASICs exist for a proof-of-work function, both goals are placed in jeopardy. Because of this, a proof-of-work function that is ASIC-resistant (i.e. difficult or economically inefficient to implement in specialised compute hardware) has been identified as the proverbial silver bullet.

@@

\item[Ethereum Browser] (aka Ethereum Reference Client) A cross-platform GUI of an interface similar to a simplified browser (a la Chrome) that is able to host sandboxed applications whose backend is purely on the Ethereum protocol, which is known as Mist since 8 July 2016 (\citeauthor{Mist}).

@@

$G_{\mathrm{txcreate}}$ & 32000 & This is paid by all contract-creating transactions after the {\textit{Homestead transition}}.}\hypertarget{Gtxdatazero}{\\
